  
***
Useful Seurat code from Farnsworth et al, 2019.
NOTE - the below code is from v2 of Seurat. Thus much is deprecated. This is presented in case users find it helpful to get started looking at the data. However, much will need to be updated as we recommend using the latest version of Seurat, and the commands have changed.

General steps for initial filtering (not included here).
- CellRanger count used for each independent dataset
- Cell Ranger aggregate used to put all datasets together

Suerat used to:
- Normalized and scale the data.
- Regressed out UMIs and mitochondiral genes.
- Used 179 PCs based on the JackStraw analysis.
- Used 18.0 as a Resolution as this identified PGCs as a cluster and reduced singletons.
  - 17.75 lost PGCs - merged with another cluster.
- Plot and examine data.
***

```{r init, message=FALSE}

library(Seurat)
library(dplyr)

# FILTERED matrix from CellRanger
all.data <- Read10X(data.dir = "path")
all <- CreateSeuratObject(raw.data = all.data, min.cells = 0, min.genes = 0, project = "10X_all")

# Filtering - first find the mitochondria genes and stash info in MetaData
mito.genes <- grep(pattern = "^mt-", x = rownames(x = all@data), value = TRUE)
percent.mito <- Matrix::colSums(all@raw.data[mito.genes, ]) / Matrix::colSums(all@raw.data)
all <- AddMetaData(object = all, metadata = percent.mito, col.name = "percent.mito")
all <- FilterCells(object = all, subset.names = c("nGene", "percent.mito", "nUMI"), low.thresholds = c(200, -Inf, -Inf), high.thresholds = c(Inf, 0.25, 100000))

# Normalize
all <- NormalizeData(object = all, normalization.method = "LogNormalize", scale.factor = 10000)

# Find Variable Genes
all <- FindVariableGenes(object = all, mean.function = ExpMean, dispersion.function = LogVMR, x.low.cutoff = 0.0125, x.high.cutoff = 3, y.cutoff = 0.5)
length(x = all@var.genes) ## check the length to see if reasonable

# Regress
all <- ScaleData(object = all, vars.to.regress = c("nUMI", "percent.mito"), do.par = TRUE, num.cores = 4)

# Identify PCs
all <- RunPCA(object = all, pc.genes = all@var.genes, do.print = TRUE, pcs.print = 1:5, genes.print = 5, pcs.compute = 200)
all <- ProjectPCA(object = all, do.print = FALSE, pcs.store = 200)

# JackStraw to help identify the number of PCs to use
all <- JackStraw(object = all, num.pc = 200, num.replicate = 25, display.progress = TRUE,  do.par = TRUE, num.cores = 4)
jackStraw <- JackStrawPlot(object = all, PCs = 1:200)
ggsave(paste("jackStraw.pdf", sep=""), width=15, height=100, jackStraw, device = "jpeg", limitsize = FALSE)

# Cluster
all <- FindClusters(object = all, reduction.type = "pca", dims.use = 1:179, resolution = 18.0, print.output = FALSE, save.SNN = TRUE, force.recalc = TRUE)

# tSNE and UMAP
all <- RunTSNE(object = all, dims.use = 1:179)
all <- RunUMAP(object = all, reduction.use = "pca", dims.use = 1:179, min_dist = 0.555, n_neighbors = 37)

# Find all markers
all.markers <- FindAllMarkers(object = all, only.pos = TRUE, min.pct = 0.25, logfc.threshold = log(0.5))
write.csv(all.markers, file="allMarkers_GRCz11_179_18.csv")

# SAVE
saveRDS(all, file = "olig2_elavl4_GRCz11_aggNoNorm_res5group.rds")
```

```{r atlas plots, fig.height=20, fig.width=20}
# for tSNE
TSNEPlot(object = all, do.label = TRUE, no.legend = T)

# for UMAP
DimPlot(object = all, reduction.use = "umap", do.label = T, no.legend = T, do.return = F, vector.friendly = F, pt.size = 0.1, label.size = 6)

```

```{r temporal analysis, fig.height=15, fig.width=20}
# the below was used to label each sample, after CellRanger aggregate was used
sample1 <- "1_olig2_24a"
sample2 <- "2_olig2_24b"
sample3 <- "3_olig2_48a"
sample4 <- "4_elav_48b"
sample5 <- "5_olig2120a"
sample6 <- "6_olig2120b"
sample_name <- gsub(".*-", "", all@cell.names)

sample_name <- replace(sample_name, sample_name==1, sample1)
sample_name <- replace(sample_name, sample_name==2, sample2)
sample_name <- replace(sample_name, sample_name==3, sample3)
sample_name <- replace(sample_name, sample_name==4, sample4)
sample_name <- replace(sample_name, sample_name==5, sample5)
sample_name <- replace(sample_name, sample_name==6, sample6)

sample_names <- data.frame(sample_name, row.names=all@cell.names)
all <- AddMetaData(object = all, metadata = sample_names)
TSNEPlot(object = all, group.by = "sample_name", pt.size = 1, label.size = 5)

DimPlot(object = all, reduction.use = "umap", group.by = "sample_name", do.label = F, no.legend = F, do.return = F, vector.friendly = F, pt.size = 0.1)

```

```{r labelplot, fig.height=16, fig.width=20, warning = FALSE}
### Assigning cell type identity to clusters based on Dylan et al, 2019
all <- StashIdent(object = all, save.name = "ClusterNames")
# make a simple list of where we are now
current.cluster.ids <- c(0:220)
# below list corresponds to the "Ident Annotation" column of the table Table S2
new.cluster.ids <- c("Peri1a", "RetProgAlla", "MHBDiff12a", "NonspecificAlla", "MHBProg12", "Gill5a", "RBC2a", "MusSkelFast1", "HBProg1a", "MusSkelFast2a", "FBProgAlla", "MBDiff5", "MBProg12a", "MHBNeur25", "HBProg1b", "SCProg12a", "Arch2a", "antSCProg1a", "NCcart2", "HBProg1c", "antSCDiff12a", "Gill5b", "Myotome", "Basal5a", "NCcranial5a", "FBNeurInhibAll", "HBDiff1a", "MHBNeurGlutAll", "Parachord12", "NCcranial5b", "RetDiff2", "NCcranial2", "NCcranial1a", "Sclero1", "RetProg1a", "SCNeurCilia12a", "MusSkelProgAll", "RetDiff25a", "RBC1a", "SCProg12b", "FMBProgAll", "MHBProgAll", "MBDiff25", "HBProg1d", "MyoProg5a", "PharEpi1a", "PharEpi1b", "Basal2a", "RBC2b", "Nonspecific12", "NCcart5a", "HBDiff12a", "RetProg0a", "MyoProg5b", "RetProg0b", "Hepato5a", "CranGangAlla", "MusSkelSlow1a", "RetDiffAll", 
"Thymus", "RetDiff25b", "HBProgMN1e", "FBProgAllb", "RBC1b", "NCneural12", "antSCDiff12b", "HBDiff12b", "FloorplateMB1", "FMBDiff12a", "NCcardiac", "Basal1", "Macro5", "MHBDiff25", "RetNeuron25", "RetProgAllb", "HBDiff25", "MHBNeurGABAAll", "Peri2a", "Peri2b", "EndotheAlla", "NCcranial5e", "BasalFin5a", "HBDiff12c", "RetDiff25c", "MyoProg2a", "RBC2c", "MHBDiff12b", "NCcranial1b", "EndotheAllb", "FBProgAllc", "OligoFB", "FBProgAlld", "Sclero2", "Otic", "Olfactory", "SCDiff12a", "RPE", "RadialGlia2", "FinBud12", "RetProgAllc", "MesenUnk2", "IntestineEpiAll", "NCcranial1c", "MusSkelFast2b", "RetDiff25d", "CranGangAllb", "LensEpi", "RetDiff2", "BasalFin1", "RadialGlia5", "FinBud25", "MBProg12b", "SCNeurInhib12a", "RetDiff25e", "antSCProg1b", "RetPR", "MusSkelSlow25", "Vessel1", "Basal12", 
"HG1", "HBProg12", "Hepato5b", "RetProg5a", "SCDiff2", "FMBDiff12b", "FinBud5", "HBDiffMN12d", "MyoProg2b", "IonoNaK", "NCirid", "HeartTube", "HBDIff1b", "OligoFMB", "IonoNCC5a", "FBProg12", "MesenUnk5", "MHBNeurGABA12", "LatLine", "RetDiff25f", "HBDiff1c", "Arch12", "LensAll", "FBDiffAll", "SCNeurMN12b", "Kidney", "BasalFin12", "Gill5c", "HeartPrimord", "NCcart5b", "Notochord25", "Neutrophil", "MHBDiff1", "IntestineEpi5a", "RBCProgAll", "MusCeph", "Tailbud", "NCxantho1", "RBC5", "Notochord1", "NonspecificAll", "SCDiff12c", "NCcranial1d", "Spleen", "Roofplate", "NCcranial1e", "IonoNCC5b", "antSCProg1c", "Vessel2", "IntestineEpi5b", "MucNCC", "NCcranial5c", "MusVascSmo", "HBDiff2", "NCneural25", "NCmel1", "PlacodalUnk", "FloorplateSCAll", "RetNeuron5", "NCmel25", 
"PharEpi2", "PancExo", "NCcranial5d", "Peri2c", "Peri1b", "Macro12", "NCxantho25", "Basal5b", "Nonspecific1a", "BasalFin5b", "PancAB", "Peri1c", "Parachord1", "FBDiff12", "Nonspecific1b", "SCDiff12c", "MHBProg1", "TasteBud", "MusEntSmo", "HairCell", "Hypophysis", "Lens12", "Vessel5", "SCNeurCilia12b", "Arch2b", "FinBud2", "MusCard", "Basal2b", "HG2", "IonovH", "MusSkelSlow1b", "SpleenEpi", "Epiphysis", "Macro1", "Endothe1", "IntestineEpi1", "Peri1d", "Osteo", "Hepato5c", "Hypochord", "PGC", "Nonspecific")
# apply these names to the Atlas map for viewing - the naming of the current object clusters must be 0:220 for the below to work
all@ident <- plyr::mapvalues(x = all@ident, from = current.cluster.ids, to = new.cluster.ids)
# view with the new annotations
DimPlot(object = all, reduction.use = "umap", do.label = T, no.legend = T, do.return = F, vector.friendly = F, pt.size = 0.1, label.size = 5)
#restore to the numbering system (0:220)
# this allows for updating of the above list of names as appropriate
all <- SetAllIdent(object = all, id = "ClusterNames")
```

```{r Feature Plots, fig.height=16, fig.width=20, warning=FALSE}

# top16 most differential genes (pct1/pct2) for all clusters in the Atlas
## cluster numbers and names match TableS2
# cluster 0 - Peri1a - 
FeaturePlot(all, features.plot = c("he1.3", "ftr14l", "cyp2aa8", "cyp2aa11", "si:ch211-264e16.1", "si:dkeyp-87d8.8", "si:dkey-160o24.3", "BX569789.1", "zgc:113442", "zgc:194839", "nos1", "tgm1l4", "CABZ01049361.1", "si:ch211-202h22.8", "nadka", "si:dkeyp-4c4.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 1 - RetProgAlla - 
FeaturePlot(all, features.plot = c("vsx2", "rx1", "six3b", "si:dkey-238o13.4", "col15a1b", "stra6", "nr2e1", "myb", "wfdc1", "tbx2a", "crip3", "hmx4", "pax6b", "cart3", "AL954322.2", "zic2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 2 - MHBDiff12a - 
FeaturePlot(all, features.plot = c("her3", "en2b", "sfrp1a", "sp8b", "dbx1b", "efna2a", "dbx1a", "wfikkn1", "sox21a", "col5a3a", "sema3fa", "npas1", "st8sia2", "sfrp5", "irx1a", "prtgb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 3 - NonspecificAlla - 
FeaturePlot(all, features.plot = c("en2b", "sox19a", "paics", "cmss1", "her8a", "esco2", "sox3", "nusap1", "umps", "ftsj3", "rrm2", "pclaf", "mcmbp", "nasp", "parp1", "ddx24"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 4 - MHBProg12 - 
FeaturePlot(all, features.plot = c("dmbx1a", "pax7a", "en2b", "pax7b", "en2a", "efna2a", "hey2", "otx2b", "pax3a", "sema3fa", "foxn4", "otx2a", "fzd10", "irx1a", "mab21l2", "pou3f3a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 5 - Gill5a - 
FeaturePlot(all, features.plot = c("urgcp", "plekhs1", "si:dkey-201i2.1", "AL928650.1", "si:ch211-266a5.12", "si:dkey-187j14.4", "ca15c", "si:dkey-239b22.1", "si:dkey-238k10.2", "cyldb", "CABZ01051602.1", "vwa10.1", "CU914622.2", "rhcgl1", "zgc:194007", "si:ch73-329n5.6"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 6 - RBC2a - 
FeaturePlot(all, features.plot = c("gp9", "rfesd", "hif1al2", "zgc:163057", "si:ch211-207c6.2", "si:ch211-250g4.3", "si:dkey-93h22.7", "si:ch73-250a16.5", "nmt1b", "hbae5", "si:ch211-227m13.1", "epb41b", "alas2", "rell2", "CR293511.1", "nt5c2l1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 7 - MusSkelFast1 - 
FeaturePlot(all, features.plot = c("rtn2a", "obsl1a", "klhl40b", "prp", "dhrs7ca", "p2rx5", "klhl43", "neurl2", "FO818704.2", "zgc:113276", "xirp2b", "obscnb", "tgm2a", "slc8a3", "CU929145.2", "cacna1sb"), cols.use = c("light gray", "red"), reduction.use = "umap")
### below differenetiates slow and fast muscle
  FeaturePlot(allSUB, features.plot = c("sox6", "mylpfa", "mylpfb", "myhz1.1", "myhz1.2", "myhz1.3", "myhz2", "smyhc1", "smyhc2", "smyhc3", "tnnc1b", "prox1a", "mybpc1", "tnnc1a", "tnnc2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 8 - HBProg1a - 
FeaturePlot(all, features.plot = c("atoh1a", "olig4", "olig3", "egr2b", "nog2", "cdh6", "msx3", "epha4l", "fibinb", "atoh8", "msx1b", "zic2b", "irx1b", "bmp5", "draxin", "rfx4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 9 - MusSkelFast2a - 
FeaturePlot(all, features.plot = c("hspb2", "capn3b", "CABZ01061524.1", "pbld2", "hsc70", "pfkma", "tmem41ab", "glra4a", "igfn1.3", "synpo2b", "pfkmb", "CU693479.1", "kbtbd12", "cdnf", "myha", "abrab"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 10 - FBProgAlla - 
FeaturePlot(all, features.plot = c("foxg1a", "fezf1", "gsx2", "emx3", "fezf2", "sox1b", "lhx2b", "lmo1", "cyp26c1", "CR848047.1", "LO018196.1", "mcama", "six3a", "auts2b", "CU467822.1", "zgc:165461"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 11 - MBDiff5 - SOME EYE PROGRAM - epiphysis?
FeaturePlot(all, features.plot = c("en2a", "fsta", "atp1b4", "slc3a2a", "znf219", "atp1a1b", "BX324164.4", "ctrl", "c6ast4", "opn1sw1", "cpa5", "ela2l", "gngt2b", "ptgdsb.2", "arr3b", "ctrb1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 12 - MBProg12a - 
FeaturePlot(all, features.plot = c("shox2", "otx2a", "zgc:101100", "dbx1a", "barhl2", "CR751602.2", "robo4", "nr2e1", "foxb1a", "otx2b", "tcf7l2", "pou3f2b", "irx1b", "BX569787.1", "otx1", "mapk12b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 13 - MHBNeur25 - 
FeaturePlot(all, features.plot = c("dpf1", "pou4f1", "kif3cb", "diras1a", "sprn", "ppp1r14ba", "si:ch211-10a23.2", "atl1", "camk2d2", "si:dkey-12h9.6", "nell2b", "nmnat2", "si:dkey-56f14.7", "BX927184.1", "si:dkeyp-117h8.2", "atat1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 14 - HBProg1b - 
FeaturePlot(all, features.plot = c("lbx1b", "gsx1", "pax7b", "si:ch73-364h19.1", "pax7a", "sox21a", "prdm8", "auts2b", "pax3a", "cyp26b1", "robo4", "hoxa2b", "mapk12b", "rfx4", "CR751602.2", "wnt7aa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 15 - SCProg12a - 
FeaturePlot(all, features.plot = c("cdx4", "ldlrad2", "si:ch73-265d7.2", "hoxb9a", "hoxc8a", "hoxb8a", "hoxa9a", "hoxc6b", "ptprz1b", "si:ch211-170d8.2", "col28a2a", "dbx1b", "hoxd3a", "hoxc1a", "wnt4a", "hoxb7a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 16 - Arch2a - 
FeaturePlot(all, features.plot = c("gsc", "lhx6", "foxl1", "barx1", "foxf2a", "prrx1b", "hand2", "pax9", "fgfbp2b", "twist1b", "fli1a", "LO018188.1", "six1a", "fibina", "phldb2b", "prrx1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 17 - antSCProg1a - 
FeaturePlot(all, features.plot = c("olig3", "gsx2", "olig4", "hoxd4a", "zic4", "prss35", "zic1", "zic6", "irx1b", "zic5", "rxrga", "hoxc1a", "fzd10", "msx3", "pax3a", "zic2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 18 - NCcart2 - 
FeaturePlot(all, features.plot = c("col9a1a", "ccdc3b", "fgfbp2b", "col11a2", "enpp6", "col9a3", "foxf2a", "six2a", "cthrc1a", "col9a2", "cpxm1a", "fibina", "foxc1b", "angptl1a", "cd248a", "twist2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 19 - HBProg1c - 
FeaturePlot(allSUB, features.plot = c("egr2b", "olig3", "msx1a", "zic5", "irx1b", "zic4", "msx3", "olig4", "zic1", "fzd10", "si:ch73-364h19.1", "zic2b", "pax3a", "zic2a", "rfx4", "CR751602.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 20 - antSCDiff12a - 
FeaturePlot(all, features.plot = c("hoxd4a", "sox21a", "gbx1", "rxrga", "foxb1a", "dbx1b", "wfikkn1", "sp8a", "plekhh1", "sulf2a", "mapk12b", "si:ch73-265d7.2", "raraa", "her8.2", "CR382300.1", "hoxb5b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 21 - Gill5b - 
FeaturePlot(all, features.plot = c("CR626884.5", "cyldb", "si:dkey-238k10.2", "si:dkey-202l22.6", "si:dkey-239b22.1", "caspbl", "plekhs1", "zgc:152791", "si:ch73-329n5.6", "AL928650.1", "si:ch211-266a5.12", "si:dkey-7c18.24", "rhcgl1", "si:ch211-226h7.3", "si:dkey-201i2.1", "btr21"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 22 - Myotome - 
FeaturePlot(all, features.plot = c("dmrt2a", "myf5", "wnt2", "fgl1", "col6a4a", "rbp7b", "COMP", "tcf15", "rprmb", "fbln7", "meox1", "cilp", "tril", "thbs4b", "csf1a", "mxra5a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 23 - Basal5a - 
FeaturePlot(all, features.plot = c("si:dkey-91f15.1", "ccl27a", "col17a1a", "htra4", "plek2", "entpd3", "sod3b", "cxcl18a.1", "CABZ01044281.1", "mmp30", "ms4a17a.4", "si:ch211-76l23.4", "si:dkey-95h12.1", "b3gnt5b", "rasgrp4", "cxl34b.11"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 24 - NCcranial5a - 
FeaturePlot(all, features.plot = c("aspn", "rgs5a", "hpdb", "fstl3", "tat", "zgc:153704", "CABZ01092746.1", "ttc36", "cldn11a", "ifitm1", "abi3bpb", "angptl1a", "fstb", "asip2b", "zgc:174904", "ms4a17a.7"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 25 - FBNeurInhibAll - 
FeaturePlot(all, features.plot = c("arxb", "dlx2b", "arxa", "dlx1a", "gad2", "sp9", "si:dkey-175g6.2", "nrxn3a", "slc32a1", "gad1b", "dlx6a", "slc6a1b", "nkx2.1", "gria1a", "celf4", "gas7a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 26 - HBDiff1a - 
FeaturePlot(all, features.plot = c("her3", "dbx1b", "dbx1a", "robo4", "egr2b", "sox21a", "gbx1", "wfikkn1", "cyp26b1", "hoxa2b", "si:ch73-364h19.1", "sp8b", "wnt7aa", "scube2", "sulf2a", "foxb1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 27 - MHBNeurGlutAll - 
FeaturePlot(all, features.plot = c("si:dkey-10f21.4", "stmn3", "slc17a6a", "zgc:153615", "nos1apb", "ppp2r2ca", "syn1", "sncgb", "si:ch211-113g11.6", "adcyap1r1a.1", "grin1a", "cacng2a", "scn8aa", "glra3", "atp2b3a", "gphnb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 28 - Parachord12 - 
FeaturePlot(all, features.plot = c("thbs3b", "ccdc80l1", "FO704741.1", "ccdc80l2", "si:ch211-160j14.3", "apof", "alx4a", "zgc:162612", "csf1a", "si:ch211-69b22.5", "cthrc1a", "pcolcea", "csf1b", "ndnfl", "col9a1a", "tbx15"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 29 - NCcranial5b - 
FeaturePlot(all, features.plot = c("aspn", "gsc", "CABZ01092746.1", "dkk3b", "cldn11a", "hpdb", "zgc:153704", "rgs5a", "ecrg4a", "si:dkey-12l12.1", "angptl1a", "abi3bpb", "asip2b", "fstl3", "mxra8b", "ccdc3b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 30 - RetDiff2 - 
FeaturePlot(all, features.plot = c("hes2.2", "six6b", "si:dkey-238o13.4", "cldn5b", "foxn4", "si:ch73-215f7.1", "vsx2", "ascl1a", "slc38a3a", "rx1", "foxg1b", "myb", "crip3", "nr2e1", "mybl1", "dlc"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 31 - NCcranial2 - 
FeaturePlot(all, features.plot = c("spon2b", "dlx4a", "dlx6a", "dlx4b", "barx1", "fgfbp2b", "dlx1a", "dlx2a", "dlx5a", "foxc1b", "grem2b", "fli1a", "phlda3", "emx2", "dlx3b", "fibina"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 32 - NCcranial1a - 
FeaturePlot(all, features.plot = c("ednrab", "fgf20b", "grem2b", "barx1", "dlx4b", "dlx6a", "dlx1a", "pdgfbb", "dlx2a", "phlda3", "cxcr4a", "foxc1b", "vasna", "twist3", "angptl2b", "fli1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 33 - Sclero1 - 
FeaturePlot(all, features.plot = c("nkx3-1", "aplnr2", "vcanb", "pax9", "c7a", "rbp7b", "COMP", "meox1", "tcf15", "angptl7", "mxra5a", "twist2", "tril", "emilin2b", "vwde", "cilp"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 34 - RetProg1a - 
FeaturePlot(all, features.plot = c("rx2", "vsx2", "rx1", "hist1h2a5", "hist1h2a11.4", "zgc:165555", "CR354435.2", "si:dkey-108k21.21", "si:dkey-108k21.19", "hmx1", "nr2e1", "si:ch1073-153i20.5", "si:dkey-261m9.12", "si:ch211-113a14.24", "hist1h2a2.1", "si:ch1073-153i20.4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 35 - SCNeurCilia12a - 
FeaturePlot(all, features.plot = c("rsph9", "cfap52", "spag6", "tbata", "cfap126", "si:ch211-153f2.7", "armc4", "si:ch211-163l21.10", "si:dkeyp-110a12.4", "pih1d2", "spata18", "si:ch211-163l21.7", "cdx4", "lrrc6", "si:dkey-148f10.4", "lrrc23"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 36 - MusSkelProgAll - 
FeaturePlot(all, features.plot = c("mymk", "filip1a", "flncb", "cdh15", "klhl40b", "asb12b", "BX649294.1", "chrng", "CR925737.1", "trim109", "FO818704.2", "mss51", "alpk3b", "AL772146.2", "klhl40a", "tmx2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 37 - RetDiff25a - 
FeaturePlot(all, features.plot = c("atoh7", "tfap2d", "prdm1b", "ndrg1b", "hes2.2", "foxn4", "mybl1", "otx2b", "slc38a3a", "foxg1b", "cspg5b", "ptprua", "bhlhe22", "tbx2b", "six6b", "neurod4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 38 - RBC1a - 
FeaturePlot(all, features.plot = c("CR854926.1", "tfr1a", "drl", "CR388184.1", "susd1", "gfi1b", "slc10a4", "fech", "si:dkey-261j4.3", "si:dkey-150i13.2", "gpr78a", "tbx16l", "cyp46a1.1", "nfe2", "gata1a", "ppox"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 39 - SCProg12b - 
FeaturePlot(all, features.plot = c("lbx1b", "hoxc8a", "hoxc9a", "hoxb6b", "prdm13", "hoxc6b", "ldlrad2", "wnt4a", "hoxa9a", "hoxb9a", "hoxb8a", "si:ch211-67e16.11", "si:dkeyp-110a12.4", "prss35", "hoxc1a", "olig3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 40 - FMBProgAll - 
FeaturePlot(all, features.plot = c("si:ch211-69b22.5", "zic6", "wnt8b", "tpbga", "otx1", "otx2a", "rspo2", "cep112", "barhl2", "zic4", "zic5", "wnt4a", "sp5a", "tnfrsf19", "clybl", "otx2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 41 - MHBProgAll - 
FeaturePlot(all, features.plot = c("pax5", "en1a", "en2a", "en1b", "fgf8a", "slf1", "gbx2", "atoh1a", "pax2a", "en2b", "sp9", "oc90", "olig3", "tubb2", "ism1", "il17rd"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 42 - MBDiff25 - 
FeaturePlot(all, features.plot = c("helt", "zgc:101100", "hs3st1l2", "CU929451.2", "masp1", "CR848047.1", "ptprz1a", "gsx1", "si:ch73-215f7.1", "otx2b", "pax7a", "ascl1b.1", "cep112", "nfia", "znf219", "nr2e1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 43 - HBProg1d - 
FeaturePlot(all, features.plot = c("mpz", "egr2b", "nkx6.2", "gbx1", "sox21a", "cyp26b1", "nkx6.1", "sulf2a", "hoxa2b", "wfikkn1", "foxb1a", "CR848812.1", "prdm12b", "sulf2b", "prdm8", "sfrp1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 44 - MyoProg5a - 
FeaturePlot(all, features.plot = c("msc", "col18a1b", "myf5", "myog", "myod1", "txnipb", "jam2a", "vwde", "jam2b", "chrna1", "zgc:92518", "cyp2n13", "pitx3", "hsp90aa1.1", "mafaa", "tcf15"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 45 - PharEpi1a - 
FeaturePlot(all, features.plot = c("pax1b", "si:dkey-43p13.5", "pax1a", "nkx2.7", "fgf17", "foxi1", "nkx2.3", "frem2a", "shhb", "foxa2", "fgf24", "irx7", "tbx1", "ptprfa", "sostdc1a", "fgfrl1b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 46 - PharEpi1b - 
FeaturePlot(all, features.plot = c("foxi1", "vgll4l", "padi2", "si:ch211-67e16.11", "ppp1r1b", "kera", "fermt1", "lrata", "cldn1", "col7a1", "zgc:171775", "col14a1a", "zgc:101810", "sostdc1a", "ecrg4b", "si:ch211-202f3.3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 47 - Basal2a - 
FeaturePlot(all, features.plot = c("si:ch211-256a21.4", "si:dkey-95h12.1", "col28a1a", "col17a1a", "CU459012.1", "zgc:100997", "si:ch211-241e1.3", "col17a1b", "lamb4", "entpd3", "si:ch211-213d14.2", "col5a3b", "lrata", "zgc:113223", "c7a", "si:ch211-76l23.4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 48 - RBC2b - 
FeaturePlot(all, features.plot = c("BX005417.1", "si:ch73-288o11.4", "si:ch211-250g4.3", "gp9", "hsp70l", "CR293511.1", "si:ch211-207c6.2", "zgc:163057", "nmt1b", "cabp2a", "hbae5", "epb41b", "fbxo32", "slc20a1a", "alas2", "nt5c2l1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 49 - Nonspecific12 - 
FeaturePlot(all, features.plot = c("crip3", "six3b", "prmt3", "umps", "fabp11a", "myca", "tjp2b", "rnaseh2b", "kmt5ab", "chchd10", "cmss1", "kpna2", "hgh1", "atic", "mcmbp", "aprt"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 50 - NCcart5a - 
FeaturePlot(all, features.plot = c("otos", "tnmd", "angptl5", "ucmab", "epyc", "adgrg6", "cpxm1a", "col9a1a", "col11a2", "aspn", "angptl1a", "fstl3", "zgc:153704", "zgc:113307", "pigr", "col9a3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 51 - HBDiff12a - 
FeaturePlot(allSUB2, features.plot = c("AL845362.1", "lbx1b", "prdm13", "gsx2", "tfap2b", "BX530077.1", "kirrel3l", "ascl1a", "pax3a", "zic1", "draxin", "pcdh1g32", "zic4", "hoxd4a", "CR848812.1", "zic2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 52 - RetProg0a - 
FeaturePlot(all, features.plot = c("vsx2", "rx1", "si:dkey-238o13.4", "hmx4", "six3b", "crip3", "si:dkey-261m9.12", "tjp2b", "fabp11a", "umps", "si:dkey-108k21.10", "exosc8", "pax6b", "rnaseh2b", "trmt6", "myca"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 53 - MyoProg5b - 
FeaturePlot(all, features.plot = c("si:ch211-287a12.9", "clec3ba", "fgl1", "cldn7a", "olfml2bb", "myf5", "admb", "dmrt2a", "ackr3a", "fbln7", "rbp7b", "zgc:113307", "thbs4b", "cilp", "si:ch211-243a20.3", "csf1b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 54 - RetProg0b - 
FeaturePlot(all, features.plot = c("rx1", "six3b", "foxd1", "fabp11a", "fahd1", "umps", "cx43", "myca", "prmt3", "cmss1", "zgc:194224", "dctpp1", "ftsj3", "exosc8", "ddx51", "atic"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 55 - Hepato5a - 
FeaturePlot(allSUB, features.plot = c("cbln14", "si:ch211-113d11.5", "zgc:171534", "or109-11", "serpina7", "cbln5", "cbln9", "ccl39.2", "zgc:172253", "cpb2", "ahsg1", "si:ch211-262h13.5", "si:ch73-15n24.1", "si:dkey-96f10.1", "itih2", "si:dkeyp-73d8.6"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 56 - CranGangAlla - 
FeaturePlot(all, features.plot = c("pvalb6", "zgc:158291", "tlx2", "cerkl", "isl2b", "rab3db", "gfra1a", "six2b", "ngfrb", "six4b", "stk25a", "phox2a", "isl2a", "msi2a", "neurod1", "eya2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 57 - MusSkelSlow1a - 
FeaturePlot(all, features.plot = c("si:dkeyp-68b7.10", "CU896691.1", "kcnmb2", "si:ch211-28p3.4", "CU633479.2", "smyhc3", "klhl41a", "actn2b", "smyhc2", "rnf207b", "myh7bb", "mylk3", "BX088524.3", "myom1b", "tnni1d", "ryr1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 58 - RetDiffAll - 
FeaturePlot(all, features.plot = c("atoh7", "mybl1", "hes2.2", "foxn4", "dlc", "bhlhe22", "six6b", "foxg1b", "pou2f2a.1", "rx1", "vsx1", "onecut1", "dhx32b", "tbx2b", "insm1a", "neurod4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 59 - Thymus - 
FeaturePlot(all, features.plot = c("cytip", "si:ch211-214p16.1", "si:ch73-208g10.1", "sla2", "ccl38.6", "lpar5a", "CU019662.1", "vaspa", "si:dkeyp-68b7.12", "si:dkey-185m8.2", "prkacba", "rasal3", "ccr9a", "wipf1a", "wasa", "coro1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 60 - RetDiff25b - 
FeaturePlot(all, features.plot = c("nr2e3", "samd7", "six7", "otx5", "prdm1b", "crx", "tmx3a", "zgc:109965", "si:ch73-28h20.1", "gngt2a", "tulp1a", "pde6gb", "lhx4", "fkbp1ab", "elovl4b", "ndrg1b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 61 - HBProgMN1e - 
FeaturePlot(all, features.plot = c("nkx2.9", "nkx2.2b", "nkx6.2", "nkx2.2a", "foxa", "ntn1b", "helt", "phox2bb", "foxa2", "nkx6.1", "si:ch73-265d7.2", "sulf2b", "si:ch73-364h19.1", "ntn1a", "npas1", "wnt7aa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 62 - FBProgAllb - 
FeaturePlot(all, features.plot = c("rx3", "nkx2.4b", "nkx2.4a", "nkx2.1", "fzd8b", "six6a", "shha", "ndnfl", "si:dkeyp-110a12.4", "vax1", "sox1b", "fezf1", "six3a", "fezf2", "nrp2b", "nr2e1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 63 - RBC1b - 
FeaturePlot(all, features.plot = c("drl", "tfr1a", "si:dkey-261j4.3", "CR388184.1", "gfi1b", "CU463284.1", "susd1", "si:dkey-150i13.2", "slc10a4", "btk", "slc25a37", "ppox", "cyp46a1.1", "gata1a", "cldng", "slc9a1b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 64 - NCneural12 - 
FeaturePlot(all, features.plot = c("erbb3b", "crestin", "mov10b.1", "mmp17b", "ednrab", "sox10", "foxd3", "mcamb", "BX248318.1", "prdm12b", "ngfrb", "slc15a2", "mcf2l2", "snai1b", "CABZ01031290.1", "myo10l3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 65 - antSCDiff12b - 
FeaturePlot(all, features.plot = c("si:ch211-152f23.5", "BX530077.1", "lbx2", "her13", "prdm8", "nkx6.1", "cnksr2b", "sertad2a", "prox1a", "onecutl", "gadd45gb.1", "btbd6a", "neurog1", "LIN28A", "pcdh1g32", "inavaa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 66 - HBDiff12b - 
FeaturePlot(all, features.plot = c("BX530077.1", "dbx1a", "dbx1b", "otpb", "onecutl", "neurog1", "her13", "gadd45gb.1", "inavaa", "ascl1b.1", "nhlh2", "prox1a", "neurod4", "sp8b", "srrm4", "cbfa2t2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 67 - FloorplateMB1 - 
FeaturePlot(all, features.plot = c("foxa2", "foxa", "shha", "foxa1", "shhb", "ntn1b", "ldlrad2", "nkx6.2", "pitx3", "spon1b", "otx2a", "lmx1bb", "ntn1a", "npas1", "ascl1b.1", "otx1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 68 - FMBDiff12a - 
FeaturePlot(all, features.plot = c("emx1", "tbr1b", "srgap1b", "myt1la", "mpped1", "cpne2", "eomesa", "kctd4", "kcnip1b", "l1cama", "glipr1b", "PRKAR2B", "neurod6b", "khdrbs2", "olfm1a", "etv1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 69 - NCcardiac - 
FeaturePlot(all, features.plot = c("zgc:162612", "csf1a", "FO704741.1", "alx4a", "ccdc80l2", "arhgap36", "emilin1a", "npb", "csf1b", "cldn11a", "rasl11a", "foxc1a", "cthrc1a", "enpp6", "si:ch211-267e7.3", "jcada"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 70 - Basal1 - 
FeaturePlot(all, features.plot = c("itgb3a", "si:ch211-218g23.6", "si:dkey-117n7.2", "col7a1l", "thbs3a", "si:dkey-117n7.5", "col5a3b", "cpz", "CU469568.1", "def6c", "lamb4", "olfm2b", "ptger1a", "si:ch211-256a21.4", "si:dkey-91f15.8", "lrata"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 71 - Macro5 - 
FeaturePlot(all, features.plot = c("itgae.1", "c1qa", "NPC2 (1 of many)", "si:dkey-148a17.6", "zgc:103700", "marco", "c1qb", "mrc1b", "ccl35.1", "si:ch211-194m7.4", "BX682234.1", "csf2rb", "si:dkey-1h24.6", "slc2a6", "ccl34a.4", "CABZ01088134.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 72 - MHBDiff25 - 
FeaturePlot(all, features.plot = c("scrt1b", "tfap2d", "sox12", "insm1b", "zgc:162707", "stap2a", "scrt2", "mpp2a", "en2b", "lef1", "insm1a", "lhx9", "ptprua", "en2a", "lzts1", "srrm4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 73 - RetNeuron25 - 
FeaturePlot(all, features.plot = c("pax10", "si:ch73-290k24.5", "prdm13", "gad2", "tfap2b", "sox12", "barhl2", "slc32a1", "bhlhe22", "six6b", "foxg1b", "lhx9", "ndrg4", "kctd15a", "scrt1a", "pde6gb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 74 - RetProgAllb - 
FeaturePlot(all, features.plot = c("vsx2", "rx1", "hmx1", "col15a1b", "si:dkey-238o13.4", "nr2e1", "hmx4", "six3b", "myb", "six3a", "wfdc1", "crip3", "ggctb", "cart3", "dclk2a", "tbx2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 75 - HBDiff25 - 
FeaturePlot(all, features.plot = c("masp1", "CU929451.2", "AL845362.1", "CR848047.1", "atoh1a", "nfia", "si:ch73-215f7.1", "olig3", "znf219", "zic4", "zic5", "CU467822.1", "chfr", "zic1", "prss35", "zic2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 76 - MHBNeurGABAAll - 
FeaturePlot(all, features.plot = c("sprn", "aig1", "sv2a", "nell2b", "pcsk1nl", "scg2b", "eno2", "sypa", "gpr85", "kif5aa", "scg5", "si:dkey-12h9.6", "itm2ca", "lhx1a", "maptb", "atp1a3a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 77 - Peri2a  - 
FeaturePlot(all, features.plot = c("ponzr4", "BX571705.1", "si:ch211-161h7.8", "ubap1la", "wu:fj05g07", "zgc:112964", "trim35-9", "grk5", "b3gnt3.1", "cyp17a1", "si:rp71-1h20.9", "ftr86", "si:ch211-264e16.1", "jac10", "si:ch73-196i15.3", "si:dkeyp-13a3.10"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 78 - Peri2b - 
FeaturePlot(all, features.plot = c("CABZ01044023.1", "CABZ01044022.1", "CABZ01067657.1", "si:ch1073-190k2.1", "si:ch1073-340i21.3", "si:dkey-73p2.3.1", "jac10", "si:dkey-73p2.2", "si:ch73-196i15.3", "CABZ01072077.1", "CABZ01015525.1", "zgc:112964", "ponzr3", "si:dkey-239b22.2", "nos1", "zgc:171566"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 79 - EndotheAlla - 
FeaturePlot(all, features.plot = c("mrc1a", "lyve1b", "sele", "stab2", "CU927890.1", "gpr182", "rasip1", "stab1", "tie1", "myct1a", "tek", "scarf1", "si:ch211-33e4.2", "myct1b", "flt4", "clec14a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 80 - NCcranial5e - 
FeaturePlot(all, features.plot = c("cyp1c1", "slco2b1", "cldn11a", "zgc:153704", "timp4.3", "agtr2", "CABZ01092746.1", "cyp2ad2", "fstb", "serpinf1", "hpdb", "fstl3", "zgc:162612", "cyp2p7", "zgc:174904", "hgd"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 81 - BasalFin5a - 
FeaturePlot(all, features.plot = c("si:ch211-251f6.6", "cxl34b.11", "and3", "epgn", "postna", "ms4a17a.5", "ms4a17a.1", "plek2", "b3gnt5b", "mmp30", "rab42b", "si:dkey-95h12.1", "si:dkey-102c8.3", "cxcl8a", "zgc:113223", "cldn1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 82 - HBDiff12c - 
FeaturePlot(all, features.plot = c("atoh1b", "si:ch211-215d8.2", "scrt1b", "onecutl", "scrt1a", "lzts1", "nrn1a", "nkain2", "sdk1a", "gdf11", "lhx9", "uncx", "FP017274.1", "nhlh2", "pdlim5a", "mpp2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 83 - RetDiff25c - 
FeaturePlot(all, features.plot = c("zgc:112294", "zgc:103625", "rpgrip1", "slc1a8a", "opn6a", "foxq2", "CABZ01117619.1", "glmnb", "arhgap20", "si:ch211-276a17.5", "zgc:109965", "tmem136b", "rcvrna", "sez6a", "samd7", "BX957322.3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 84 - MyoProg2a - 
FeaturePlot(all, features.plot = c("myog", "myod1", "myf5", "jam2b", "tbx15", "jam2a", "pitx3", "efhd1", "hsp90aa1.1", "chrna1", "pitx2", "klhl41b", "tbx1", "zgc:92518", "unc45b", "stac3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 85 - RBC2c - 
FeaturePlot(all, features.plot = c("gp9", "hif1al2", "slc9a1b", "klf1", "BX284666.1", "tbx16l", "si:ch73-250a16.5", "si:dkey-261j4.4", "gata1a", "CR293511.1", "rfesd", "si:dkey-93h22.7", "si:ch211-250g4.3", "rell2", "fech", "epb41b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 86 - MHBDiff12b - 
FeaturePlot(all, features.plot = c("her5", "her11", "pax5", "pax2b", "en2a", "irx7", "zgc:101100", "en1b", "en2b", "rtn4r", "pax2a", "nkx6.2", "BX571942.1", "otx1", "foxb1a", "otx2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 87 - NCcranial1b - 
FeaturePlot(all, features.plot = c("nkx3.3", "foxf1", "tmem98", "hlx1", "foxf2b", "foxf2a", "isl2b", "BX088707.3", "nkx2.3", "gfra1a", "osr1", "rbpms2a", "rbpms2b", "barx1", "isl2a", "inhbaa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 88 - EndotheAllb - 
FeaturePlot(all, features.plot = c("notchl", "myct1b", "flt1", "pecam1", "si:ch211-33e4.2", "tie1", "ecscr", "myct1a", "scarf1", "rasip1", "ccm2l", "ushbp1", "micall2a", "arhgef9b", "clec14a", "f2rl2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 89 - FBProgAllc - 
FeaturePlot(all, features.plot = c("nkx2.4a", "nkx2.4b", "nkx2.1", "fezf2", "emx2", "sp5a", "emx3", "sox1b", "lhx2b", "pcdh10a", "oc90", "nrp2b", "efhd1", "nr2e1", "lhx5", "foxd2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 90 - OligoFB - 
FeaturePlot(all, features.plot = c("olig1", "nkx2.2a", "nkx2.2b", "nkx2.9", "gsx2", "vax1", "olig2", "lhx5", "foxd1", "ntn1b", "sox1b", "robo4", "wnt7bb", "nr2e1", "npas1", "podxl"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 91 - FBProgAlld - 
FeaturePlot(all, features.plot = c("eno4", "vax1", "fezf1", "sox1b", "fgf8a", "six6a", "ntn1b", "fezf2", "cyp26c1", "otpb", "six3a", "pax2a", "lhx2b", "nr2e1", "pdgfaa", "zic5"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 92 - Sclero2 - 
FeaturePlot(all, features.plot = c("aplnr2", "c7a", "pax9", "emilin2b", "agtr2", "cpxm1a", "nkx3.2", "kazald3", "zgc:154093", "wfdc2", "zgc:162612", "col5a2a", "fgfrl1b", "ednraa", "twist1b", "aebp1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 93 - Otic - 
FeaturePlot(all, features.plot = c("otomp", "bricd5", "si:ch211-80h18.1", "otog", "cldna", "si:dkey-30e9.6", "si:dkey-16l2.17", "gal3st1a", "si:dkey-222f2.1", "si:ch211-137a8.2", "zgc:112437", "atp1a1a.4", "stm", "mb", "si:ch211-243g18.2", "si:ch1073-184j22.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 94 - Olfactory - 
FeaturePlot(all, features.plot = c("ompb", "lhx2a", "si:ch73-335l21.2", "abhd2b", "cnga4", "rasd3", "got1l1", "vsig8a", "ppp1r15b", "fabp10b", "b3gat1b", "capslb", "mef2b", "fam228a", "emb", "cntn4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 95 - SCDiff12a - 
FeaturePlot(all, features.plot = c("chrna2a", "nkx1.2lb", "kcnd3", "si:ch211-215d8.2", "si:ch211-237l4.6", "sall3a", "plekho1a", "zgc:77784", "CR974456.1", "onecut2", "scube1", "onecutl", "sv2bb", "LIN28A", "sox14", "gata2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 96 - RPE - 
FeaturePlot(all, features.plot = c("cracr2ab", "si:dkey-43k4.5", "pmelb", "msnb", "slc24a5", "rlbp1a", "si:dkeyp-86d6.2", "tyrp1a", "sytl2b", "mitfa", "rlbp1b", "slc45a2", "fabp11b", "dct", "FP085398.1", "cax1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 97 - RadialGlia2 - 
FeaturePlot(all, features.plot = c("CU929451.2", "hepacama", "NPAS3", "masp1", "slc6a1b", "CR848047.1", "gpsm1a", "si:ch1073-303k11.2", "si:ch73-215f7.1", "npas1", "nfia", "chfr", "ptn", "her8.2", "ptprz1b", "lrrtm2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 98 - FinBud12 - 
FeaturePlot(all, features.plot = c("tbx5a", "tbx18", "csf1b", "hoxa13b", "bmp2a", "tbx15", "hand2", "fgf10a", "prrx1b", "hoxd11a", "hoxd12a", "twist3", "hoxd9a", "alx4a", "hoxd10a", "notum1b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 99 - RetProgAllc - 
FeaturePlot(all, features.plot = c("aldh1a3", "vax1", "bmp7b", "c1qtnf12", "rx1", "cyp27c1", "vsx2", "fezf2", "stra6", "col15a1b", "caska", "six3b", "cx43", "pou2f2a", "lhx2b", "pdzrn3b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 100 - MesenUnk2 - 
FeaturePlot(all, features.plot = c("osr2", "mkxa", "alx4a", "enpp6", "zgc:113307", "pitx2", "adma", "FQ323119.1", "cthrc1a", "lum", "calhm2", "rhoq", "cpxm1a", "pitx3", "cldn11a", "cd248a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 101 - IntestineEpiAll - 
FeaturePlot(all, features.plot = c("ihha", "pdx1", "hnf1ba", "hnf4g", "cldnc", "gata6", "cldn15a", "zgc:193726", "slc13a2", "si:ch211-248a14.8", "nr5a2", "foxa3", "aqp12", "hnf4a", "eps8l3a", "sst1.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 102 - NCcranial1c - 
FeaturePlot(all, features.plot = c("ednrab", "grem2b", "si:dkey-68o6.5", "dlx2a", "prrx1b", "twist1a", "phlda3", "prrx1a", "foxc1b", "snai1a", "tuba8l3", "snai2", "pmp22a", "rbms2b", "stxbp6", "tpm4a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 103 - MusSkelFast2b - 
FeaturePlot(all, features.plot = c("calcoco1b", "igfn1.3", "mybpha", "ankrd1b", "CABZ01070747.1", "zgc:136908", "myha", "prkg1b", "hsc70", "ampd1", "hspb6", "pfkma", "CU693479.1", "tmem41ab", "atp2a1l", "tnni2b.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 104 - RetDiff25d - 
FeaturePlot(all, features.plot = c("nr2e3", "samd7", "BX957322.3", "prdm1b", "six7", "CABZ01055522.1", "otx5", "tulp1a", "sept4a", "tmx3a", "ndrg1b", "zgc:109965", "crabp1a", "dscamb", "crx", "si:dkey-238o13.4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 105 - CranGangAllb - 
FeaturePlot(all, features.plot = c("sst6", "tppp2", "emb", "tmeff2b", "drgx", "ppp1r1c", "tlx2", "pou4f1", "zgc:158291", "ank2a", "CABZ01118738.1", "asphd1", "foxg1d", "stmn3", "six2b", "atp2b3b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 106 - LensEpi - 
FeaturePlot(all, features.plot = c("foxe3", "CR356246.1", "gja8b", "slc7a11", "prox2", "FO681288.1", "col28a1a", "vcana", "cx23", "sparcl1", "lim2.1", "pitx3", "col4a3", "pltp", "mafb", "hmx1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 107 - RetDiff2 - 
FeaturePlot(all, features.plot = c("CABZ01055522.1", "sept4a", "si:dkey-238o13.4", "crabp1a", "vsx1", "cldn5b", "cspg5b", "six6b", "hes2.2", "ptprua", "olig2", "si:ch73-215f7.1", "CR848047.1", "foxn4", "foxg1b", "sh3bgrl2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 108 - BasalFin1 - 
FeaturePlot(allSUB, features.plot = c("si:ch1073-80i24.3", "itgb3a", "msx2a", "col4a4", "CU469568.1", "cpz", "col5a3b", "lamb4", "si:ch211-241e1.3", "zgc:154006", "fgfbp1b", "olfm2b", "si:dkey-91f15.8", "myof", "col4a3", "wnt6b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 109 - RadialGlia5 - 
FeaturePlot(all, features.plot = c("atoh1c", "BX469902.1", "si:ch211-66e2.5", "hepacama", "mfge8a", "IGLON5", "ptn", "zbtb4", "eno1b", "clybl", "nfia", "zgc:194659", "cspg5b", "slc6a1b", "slc4a4a", "crtac1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 110 - FinBud25 - 
FeaturePlot(all, features.plot = c("hoxb13a", "si:dkey-202e22.2", "c1qtnf5", "hoxc13b", "hoxc13a", "hoxa13a", "hoxa13b", "CABZ01074130.1", "bmp2a", "and1", "angptl5", "angptl7", "mxra8b", "kazald3", "ttc36", "efemp2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 111 - MBProg12b - 
FeaturePlot(all, features.plot = c("dmbx1a", "zic6", "si:ch211-69b22.5", "cep112", "hs3st1l2", "hey2", "tnfrsf19", "fzd10", "BX571942.1", "pax7b", "otx1", "pax7a", "msx1a", "zic4", "en2b", "irx1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 112 - SCNeurInhib12a - 
FeaturePlot(all, features.plot = c("lbx1a", "skor1a", "zgc:77784", "si:dkey-175g6.2", "pax2b", "slc6a5", "scrt1a", "nkain2", "ssx2ipb", "si:ch211-215d8.2", "plekho1a", "pdlim5a", "zgc:165603", "hmx3a", "lhx1a", "onecutl"), cols.use = c("light gray", "red"), reduction.use = "umap")
  # are these CoLos? - 
  FeaturePlot(all, features.plot = c("gjd1a", "tjp1b", "nbeaa", "slc6a5"), cols.use = c("light gray", "red"), reduction.use = "umap", pt.size = 4)
  # not great overlap with gjd1a/tjp1b/nbeaa but there is some - it'll take a lot more digging, how about vlnplots and overlap? slc6a5 is quite tight in the Atlas - is it really THE thing that marks glycinergic neurons? if so, then I am in the right neighborhood, but might need to go "more to the left" into older cells to find the correct ones?
# cluster 113 - RetDiff25e - 
FeaturePlot(all, features.plot = c("zgc:158291", "pou6f2", "irx4a", "pou4f2", "barhl1a", "si:ch73-290k24.5", "pax10", "atoh7", "tfap2d", "rbpms2b", "inab", "kif3cb", "isl2b", "gng13b", "isl1", "pou4f1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 114 - antSCProg1b - 
FeaturePlot(all, features.plot = c("lbx1b", "gsx1", "hoxd4a", "pax7a", "angptl2b", "wnt7bb", "hoxb5b", "pax7b", "pax3a", "sox21a", "plekhg7", "prdm8", "crabp1b", "sp8a", "foxb1a", "hoxc1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 115 - RetPR - 
FeaturePlot(all, features.plot = c("rhol", "cnga1a", "rom1a", "ndufs8b", "CT573282.1", "cabp4", "si:rp71-39b20.4", "gucy2f", "si:dkeyp-57d7.4", "slc1a2a", "cngb3.1", "cnga3b", "zgc:77752", "si:ch73-352p18.4", "abca4b", "grk1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 116 - MusSkelSlow25 - 
FeaturePlot(all, features.plot = c("tnnt2e", "si:ch211-89o9.4", "CU633479.5", "zgc:195001", "tnni1d", "smyhc3", "CABZ01076669.1", "CU633479.2", "rnf207b", "map3k7cl", "ryr1a", "mybpc3", "mybpc1", "smyhc2", "hhatlb", "myh7bb"), cols.use = c("light gray", "red"), reduction.use = "umap")
FeaturePlot(all, features.plot = c("myl7"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 117 - Vessel1 - 
FeaturePlot(all, features.plot = c("tcf21", "esm1", "pitx3", "tbx1", "gfra3", "si:ch211-160j14.3", "tmem88b", "pdgfrb", "aplnra", "foxf2a", "pdgfab", "si:dkey-261h17.1", "nrp2a", "jcada", "adam8a", "ngfb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 118 - Basal12 - 
FeaturePlot(all, features.plot = c("si:dkey-18p12.4", "itgb3a", "tlx1", "arhgef25b", "dkk1a", "def6c", "cyp26a1", "lrata", "adra1d", "col4a4", "si:ch211-213d14.2", "col4a3", "wnt6b", "adam28", "nkx2.7", "nkx2.3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 119 - HG1 - 
FeaturePlot(all, features.plot = c("si:dkey-239j18.3", "si:dkey-269i1.4.1", "si:dkey-26g8.5", "zgc:174154", "zgc:174153", "he1.2", "si:dkey-269i1.4", "si:dkey-239j18.2", "ctslb", "he1.1", "zgc:174855", "si:dkey-108k21.10", "fabp11a", "exosc8", "rrm2", "cmss1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 120 - HBProg12 - 
FeaturePlot(all, features.plot = c("zgc:77784", "lhx1a", "pax2b", "scrt1a", "otpb", "FP017274.1", "si:ch211-215d8.2", "onecutl", "pax2a", "plekho1a", "mpp2a", "lzts1", "otpa", "nkain2", "zgc:162707", "lhx5"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 121 - Hepato5b - 
FeaturePlot(all, features.plot = c("si:ch211-186e20.2", "cbln17", "cyp2x10.2", "tdrd5", "apobb.2", "AL953907.1", "crp2", "igfals", "zgc:103559", "cfhl3", "uroc1", "gys2", "f9b", "acsbg1", "CR626907.1", "fgf19"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 122 - RetProg5a - 
FeaturePlot(all, features.plot = c("slc38a3a", "crabp1a", "cldn5b", "rx1", "foxn4", "foxg1b", "si:dkey-238o13.4", "six6b", "crip3", "ascl1a", "myb", "wfdc1", "aplnra", "enc3", "cx43", "si:ch73-215f7.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 123 - SCDiff2 - 
FeaturePlot(all, features.plot = c("CU929451.2", "si:dkeyp-110a12.4", "hoxc9a", "lrrc4.1", "hoxa9b", "npas1", "zgc:113531", "ldlrad2", "hoxa9a", "hoxb8a", "hoxb10a", "si:ch73-265d7.2", "hoxb9a", "hoxd9a", "CR848047.1", "hoxc8a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 124 - FMBDiff12b - 
FeaturePlot(all, features.plot = c("eomesa", "tbr1b", "emx3", "neurod6b", "foxg1a", "lhx2b", "lhx9", "fezf1", "adam22", "fezf2", "bcl11ba", "uncx4.1", "nrn1a", "znf296", "nfia", "clvs2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 125 - FinBud5 - 
FeaturePlot(all, features.plot = c("c1qtnf5", "si:ch211-14k19.8", "hoxa13b", "hoxa13a", "mxra8a", "adgrg6", "chst2b", "loxa", "si:ch211-76l23.4", "bgnb", "notum1b", "CABZ01092746.1", "tat", "pah", "timp4.3", "plcd4b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 126 - HBDiffMN12d - 
FeaturePlot(all, features.plot = c("tbx20", "CR812832.1", "phox2a", "tm6sf2", "phox2bb", "chodl", "rap1gap", "prph", "inab", "pdlim5a", "onecutl", "isl1", "si:ch211-215d8.2", "nkx6.1", "tp53bp2b", "dachb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 127 - MyoProg2b - 
FeaturePlot(all, features.plot = c("fgl1", "si:ch211-287a12.9", "fbln7", "zgc:113307", "loxa", "fap", "pdgfrl", "dmrt2a", "en1a", "pcp4l1", "spon2b", "col6a2", "col6a3", "si:ch1073-459j12.1", "stk17a", "meox1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 128 - IonoNaK - 
FeaturePlot(all, features.plot = c("kcnj1a.3", "kcnj1a.6", "kcnj1a.2", "bmp8a", "foxi3b", "foxi3a", "sstr5", "atp1b1b", "atp1a1a.2", "agrp", "CR356236.1", "si:ch73-14h1.2", "cers3a", "mal2", "prg4a", "BX000438.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 129 - NCirid - 
FeaturePlot(all, features.plot = c("unm_sa821", "CR318624.2", "si:ch73-89b15.3", "si:ch211-38m6.6", "si:ch211-256m1.8", "akap12a", "hsf5", "fhl2b", "alx4b", "zgc:110789", "emp3b", "si:dkey-197i20.6", "apoda.1", "gpnmb", "tcirg1a", "gpx2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 130 - HeartTube - 
FeaturePlot(all, features.plot = c("angptl6", "gata5", "tmem98", "gata6", "clec19a", "jam2b", "pitx1", "tmem88a", "hand2", "jcada", "sema3e", "bmp6", "pcolcea", "FQ323119.1", "col6a3", "BX005003.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 131 - HBDIff1b - 
FeaturePlot(all, features.plot = c("tm6sf2", "CR812832.1", "nkx2.2b", "phox2bb", "phox2a", "nkx2.9", "nkx2.2a", "nkx6.2", "foxa", "nkx6.1", "ntn1b", "spon1b", "fam117ab", "si:ch73-265d7.2", "CR847953.1", "ascl1b.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 132 - OligoFMB - 
FeaturePlot(all, features.plot = c("nkx2.4a", "nkx2.4b", "wnt16", "olig1", "wnt8b", "nkx2.1", "dbx1b", "shha", "lhx5", "pitx2", "ntn1b", "barhl2", "fezf2", "foxb1a", "vegfab", "olig2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 133 - IonoNCC5a - 
FeaturePlot(all, features.plot = c("si:dkey-189h5.6", "slc12a10.2", "clcn2c", "kcnj1a.1", "atp1a1a.3", "si:ch73-14h1.2", "si:ch73-359m17.9", "atp1a1a.2", "foxi3b", "prlra", "CABZ01083442.1", "BX000438.2", "prom2", "si:ch211-270g19.5", "atp1b1b", "gsto1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 134 - FBProg12 - 
FeaturePlot(all, features.plot = c("dmrt3a", "eomesa", "fezf2", "wnt8b", "lhx5", "fezf1", "si:ch211-69b22.5", "rspo3", "zic6", "emx3", "cyp26c1", "wnt7bb", "pdgfaa", "tnfrsf19", "otx1", "si:ch211-285f17.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 135 - MesenUnk5 - 
FeaturePlot(all, features.plot = c("cxcl8b.3", "agrp", "tmem98", "cxcl8b.1", "fgl2a", "nt5e", "colec11", "gcga", "lurap1", "BX901920.1", "sfrp1b", "si:ch211-106h4.12", "BX322618.1", "loxa", "krt94", "zgc:110182"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 136 - MHBNeurGABA12 - 
FeaturePlot(all, features.plot = c("zfpm2b", "nkx1.2lb", "sox14", "slc6a1b", "gad2", "tal1", "slc32a1", "lhx1a", "gata2a", "scrt1a", "si:dkey-175g6.2", "gad1b", "uncx", "gata3", "lhx5", "celf4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 137 - LatLine - 
FeaturePlot(all, features.plot = c("si:ch211-103f14.3", "fat1b", "twf2b", "si:ch211-172l8.4", "si:rp71-1c10.11", "mcf2lb", "hmx2", "six2b", "krt1-c5", "col17a1b", "si:dkey-222f2.1", "hmx3a", "si:dkeyp-110e4.11", "tagapa", "si:dkey-16l2.17", "wnt2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 138 - RetDiff25f - 
FeaturePlot(all, features.plot = c("sept4a", "ndrg1b", "CABZ01055522.1", "cspg5b", "vsx1", "crx", "fkbp1ab", "crabp1a", "ptprua", "si:dkey-238o13.4", "hes2.2", "foxn4", "foxg1b", "otx5", "otx2b", "sox12"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 139 - HBDiff1c - 
FeaturePlot(all, features.plot = c("jag1a", "prdm12b", "gbx1", "bhlhe22", "otpb", "pcdh18a", "ascl1b.1", "neurog1", "her13", "sox21a", "sulf2a", "sp8b", "prdm8", "CR848812.1", "her8.2", "BX530077.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 140 - Arch12 - 
FeaturePlot(all, features.plot = c("tbx1", "kazald2", "gfra3", "pdgfab", "meis3", "pdgfrb", "tmem88b", "prdm1a", "meox1", "si:dkey-261h17.1", "osr1", "prrx1a", "pcolcea", "sfrp2", "foxc1a", "efna5a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 141 - LensAll - 
FeaturePlot(all, features.plot = c("BX548032.3", "nags", "lim2.5", "si:ch211-254p10.2", "cryba1l2", "gja8b", "crybb1l3", "cps1", "endou2", "cryba1a", "si:ch73-111m19.2", "capn3a", "lim2.3", "cx23", "crygn1", "tmprss5"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 142 - FBDiffAll - 
FeaturePlot(all, features.plot = c("kctd4", "nkx2.4b", "nkx2.1", "nkx2.4a", "hmx2", "hmx3a", "FP085414.1", "sox1a", "ptpn5", "scg2b", "gpr85", "six6a", "nexmifb", "sox14", "sox1b", "celf4"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 143 - SCNeurMN12b - 
FeaturePlot(all, features.plot = c("chata", "slc5a7a", "mnx1", "slc18a3a", "si:ch211-247j9.1", "chodl", "chrnb4", "tac1", "lhx4", "si:ch211-113g11.6", "tmie", "ssx2ipb", "l1cama", "gfra3", "ret", "syn1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 144 - Kidney - 
FeaturePlot(all, features.plot = c("slc9a3.1", "AL929208.1", "zgc:195356", "amn", "si:dkey-194e6.1", "ggt1b", "cldn10b", "si:ch211-274f20.2", "mfsd4ab", "cubn", "c1qtnf9", "slc5a9", "hnf1bb", "pdzk1ip1", "si:dkey-39a18.1", "prr15lb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 145 - BasalFin12 - 
FeaturePlot(all, features.plot = c("itih5", "bhlha9", "tspearb", "adamtsl7", "srpx2", "sp6", "glsl", "vcana", "msx2a", "hapln3", "hhipl2", "and3", "mxc", "dkk1a", "col4a3", "dlx2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 146 - Gill5c - 
FeaturePlot(all, features.plot = c("CU062645.1", "si:dkey-56e3.2", "si:dkey-239b22.2", "si:dkey-7c18.24", "si:ch211-226h7.3", "CABZ01048956.1", "si:dkey-239b22.1", "tkta", "AL928650.1", "vwa10.1", "psmb8a", "caspbl", "jac10", "atp10b", "tmem176l.3b", "si:dkey-228d14.5"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 147 - HeartPrimord - 
FeaturePlot(all, features.plot = c("CR762480.2", "si:ch73-190f9.4", "FO704871.1", "piwil2", "astn1", "zgc:171482", "clec19a", "gata5", "pitx1", "sema3e", "emilin2b", "osr2", "col6a4a", "osr1", "si:ch211-160j14.3", "BX001014.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 148 - NCcart5b - 
FeaturePlot(allSUB, features.plot = c("itih1", "ninj2", "CLEC3A", "pcolceb", "wisp3", "acana", "mia", "matn1", "snorc", "tnxba", "arsia", "loxl4", "si:dkey-6n6.1", "chad", "ptgdsa", "si:dkey-31g6.6"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 149 - Notochord25 - 
FeaturePlot(all, features.plot = c("si:dkey-234i14.3", "si:ch211-13f8.2", "matn3b", "paqr4b", "chadla", "igsf10", "slc34a1a", "zgc:175280", "susd5", "si:dkey-31g6.6", "tbx3b", "LO018422.1", "gas2b", "tbxta", "si:dkey-6n6.1", "chad"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 150 - Notochord25 - 
FeaturePlot(all, features.plot = c("si:dkey-42l23.4", "c6ast1", "si:dkey-238m4.4", "itln1", "CR354540.1", "pigrl2.3.1", "il4", "si:ch211-8c17.2", "ch25hl2", "si:ch73-170d6.3", "ANPEP (1 of many)", "si:dkey-53k12.1", "ctss1", "glipr1a", "dennd3b", "si:dkey-19b23.14"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 151 - MHBDiff1 - 
FeaturePlot(all, features.plot = c("helt", "zgc:101100", "gsx1", "otx2a", "gata2a", "BX530077.1", "tfap2e", "ascl1b.1", "inavaa", "gadd45gb.1", "nkx2.2a", "her13", "otx1", "CR751602.2", "ascl1a", "nes"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 152 - IntestineEpi5a - 
FeaturePlot(all, features.plot = c("enpp7.1", "si:ch211-142d6.2", "slc28a1", "sult1st2", "cpo", "alpi.2", "rh50", "mogat2", "si:ch211-113d11.6", "adgrg4a", "apoa4b.3", "slc34a2a", "zgc:136472", "zgc:154142", "ace2", "chs1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 153 - RBCProgAll - 
FeaturePlot(all, features.plot = c("fermt3b", "top1", "s1pr5b", "tagapb", "si:ch211-103n10.5", "TCIM (1 of many)", "drl", "zar1", "hif1al2", "si:dkey-261j4.4", "lrrc15", "si:dkey-93h22.7", "si:dkey-261j4.3", "si:cabz01074946.1", "cldng", "klf1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 154 - MusCeph - 
FeaturePlot(all, features.plot = c("zgc:66156.1", "fhl5", "FO704758.1", "zgc:172270", "tnni2a.2", "trim54", "sync", "mybpc2a", "myhb", "tnni2a.3", "smpdl3b", "myhz1.1.1", "mybpc1", "mybpha", "zgc:136908", "pdlim3a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 155 - Tailbud - 
FeaturePlot(all, features.plot = c("si:ch211-196c10.11", "si:dkey-14o18.1", "hoxb13a", "hoxc13b", "hoxc12b", "hoxa13a", "hoxc13a", "sp5l", "efemp2b", "hoxd13a", "hoxa13b", "BX005254.4", "angptl2a", "pcdh8", "c1qtnf5", "msgn1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 156 - NCxantho1 - 
FeaturePlot(all, features.plot = c("sprb", "zgc:113337", "slc2a15a", "zgc:113142", "mlphb", "bscl2l", "pts", "plin6", "cax1", "si:dkey-251i10.2", "cyb561a3b", "aox5", "slc22a7a", "tmem130", "slc2a15b", "ednrba"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 157 - RBC5 - 
FeaturePlot(all, features.plot = c("si:ch211-103n10.5", "si:ch211-250g4.3", "nt5e", "slc6a22.2", "si:ch211-207c6.2", "alas2", "hif1al2", "zgc:163057", "MFAP4 (1 of many).10", "CR293511.1", "epb41b", "hemgn", "nmt1b", "nt5c2l1", "hbae5", "klf1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 158 - Notochord1 - 
FeaturePlot(all, features.plot = c("wu:fc23c09", "susd5", "si:ch211-13f8.2", "paqr4b", "chadla", "si:dkeyp-118a3.2", "LO018422.1", "tbx3b", "matn3b", "igsf10", "si:dkey-6n6.1", "tbxta", "loxl5b", "gas2b", "si:dkey-234i14.3", "adra2da"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 159 - NonspecificAll - 
FeaturePlot(all, features.plot = c("NC_002333.17", "pax6b", "mt-nd5", "fabp11a", "aifm1", "CT027638.1", "cad", "zgc:158463", "pola1", "cox17", "si:ch211-282b22.1", "ddx24", "CU467861.1", "mt-nd3", "ddx21", "pclaf"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 160 - SCDiff12c - 
FeaturePlot(all, features.plot = c("pkd1b", "cdx4", "exd1", "grm2b", "fhdc1", "jag1a", "si:dkeyp-110a12.4", "pou3f2a", "ldlrad2", "prdm12b", "dbx1b", "lrrc4.1", "lbx1b", "si:ch211-170d8.2", "mb21d2", "hoxc9a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 161 - NCcranial1d - 
FeaturePlot(all, features.plot = c("npb", "ednrab", "sema3e", "cxcr4a", "arhgap36", "ccdc80l2", "jcada", "cxcl12b", "prrx1b", "CU570769.1", "csf1a", "grem2b", "twist3", "inka1a", "ednraa", "fli1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 162 - Spleen - 
FeaturePlot(all, features.plot = c("lepb", "BX511186.1", "si:ch1073-110a20.7", "irak3", "tnfaip2b", "saa", "si:ch211-198c19.3", "cxcl8a", "steap4", "snap23.2", "si:ch211-132p1.3", "ms4a17a.10", "BX908750.1", "tlr5b", "ch25h", "hamp"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 163 - Roofplate - 
FeaturePlot(all, features.plot = c("lmx1a", "si:dkey-1c11.1", "BX469902.1", "hepacama", "fabp7b", "zgc:114181", "bcl6b", "AL928901.1", "bmp2a", "lmx1ba", "gdpd5a", "ppfibp2a", "cfap45", "rspo2", "si:ch211-66e2.5", "cfap99"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 164 - NCcranial1e - 
FeaturePlot(all, features.plot = c("irx6a", "si:dkey-250k10.4", "ednrab", "crestin", "artnb", "mmp17b", "fgf10a", "prdm1a", "pdgfbb", "gfra3", "gpc1b", "apela", "phlda3", "prrx1b", "grem2b", "meis3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 165 - IonoNCC5b - 
FeaturePlot(all, features.plot = c("si:ch211-180m24.3", "zgc:165423", "calhm1", "si:dkeyp-75b4.8", "pkhd1l1", "nox1", "CT030129.1", "si:ch1073-155h21.1", "si:ch73-329n5.1", "hhla2b.1", "ca15c", "mslna", "krt1-19d", "MFAP4 (1 of many).7", "ca15a", "cyldb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 166 - antSCProg1c - 
FeaturePlot(all, features.plot = c("hoxb6b", "hoxb5b", "hoxb6a", "dhrs3b", "hoxc1a", "hoxb1b", "prdm8", "hoxb5a", "ncam1b", "si:ch73-265d7.2", "sulf2a", "hoxd4a", "foxb1a", "foxb1b", "sox21a", "rxrga"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 167 - Vessel2 - 
FeaturePlot(all, features.plot = c("si:dkeyp-106c3.1", "zgc:158423", "fpr1", "FO704741.1", "apof", "lamc3", "cldn11a", "zgc:162612", "ndnfl", "tgm2l", "chst2b", "si:ch211-160j14.3", "calcrla", "CABZ01073265.1", "osr1", "pdgfrl"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 168 - IntestineEpi5b - 
FeaturePlot(all, features.plot = c("tspan34", "si:ch211-202h22.9", "plac8.2", "itga6l", "si:dkey-188i13.9", "zgc:77748", "cdx1b", "ca4b", "ccl25a", "zgc:136872", "zgc:158432", "anxa2b", "clrn3", "zgc:198329", "si:ch73-194h10.2", "cldn15la"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 169 - MucNCC - 
FeaturePlot(all, features.plot = c("BX649522.1", "st6galnac1.1", "zgc:112433", "muc5.2", "muc5.1", "si:dkey-65b12.6", "slc46a3", "si:ch211-163l21.8", "fev", "si:dkey-246j7.1", "pou2f3", "p2rx1", "s1pr5b", "st6gal2b", "C1GALT1 (1 of many).1", "fam83fa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 170 - NCcranial5c - 
FeaturePlot(all, features.plot = c("cald1b", "si:ch211-286f9.2", "rgs5a", "rgs4", "twist2", "frzb", "postna", "asip2b", "tat", "vcanb", "si:dkey-12l12.1", "pah", "aspn", "si:ch211-106h4.12", "hpdb", "ttc36"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 171 - MusVascSmo - 
FeaturePlot(all, features.plot = c("pdlim3a", "csrp1b", "desmb", "mylkb", "gucy1a1", "cabp1a", "CR848749.2", "fhl1a", "cald1b", "CU571069.1", "smtna", "zgc:110699", "myh11a", "BX908750.1", "kcne4", "pde9a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 172 - HBDiff2 - 
FeaturePlot(all, features.plot = c("sox14", "cyp2aa2", "gata2a", "vsx1", "hes2.2", "foxn4", "si:ch211-117c9.5", "cited1", "lhx1a", "ptprua", "gdf11", "cdkn2c", "CR848844.1", "bhlhe22", "golga7ba", "foxp2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 173 - NCneural25 - 
FeaturePlot(all, features.plot = c("si:ch211-197g15.7", "zwi", "scn4ab", "hepacama", "dkk1a", "nr4a2b", "hbegfb", "sox10", "zgc:112437", "mcamb", "adgrg6", "foxd3", "ccdc80", "pcdh7a", "ngfrb", "tp53i11b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 174 - NCmel1 - 
FeaturePlot(all, features.plot = c("opn5", "tyr", "slc24a5", "tspan10", "si:dkey-24c2.9", "ednrba", "crestin", "cdk15", "aqp7", "slco1c1", "zgc:91968", "pts", "rab34b", "tmem125b", "cax1", "emp3b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 175 - PlacodalUnk - 
FeaturePlot(all, features.plot = c("si:ch211-256e16.6", "zgc:112408", "vill", "gfral", "CABZ01073083.1", "gbgt1l3", "si:ch211-130m23.2", "st3gal1l2", "gng8", "zgc:101731", "CR759836.1", "gcnt7", "ddx4", "tph1b", "prr15la", "cx28.8"), cols.use = c("light gray", "red"), reduction.use = "umap")
  # great gene below for Proneph
  FeaturePlot(all, features.plot = c("ndrg1a"), cols.use = c("light gray", "red"), reduction.use = "umap", pt.size = 2)
# cluster 176 - FloorplateSCAll - 
FeaturePlot(all, features.plot = c("wnt4b", "urp2", "vwa3a", "spon1a", "gucy1a1", "rnf32", "s100b", "cdkl1", "cfap157", "tbata", "slit1b", "si:ch211-215c18.3", "npr3", "morn3", "shhb", "ccdc169"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 177 - RetNeuron5 - 
FeaturePlot(all, features.plot = c("si:ch211-13f8.1", "lrit1a", "nyx", "gabra4", "gabrr2a", "RIC3", "cabp5a", "igsf21b", "si:ch211-232m10.6", "nrn1lb", "mfsd2b", "rgs11", "FAM163A", "lactbl1b", "trpm1a", "si:ch211-160f23.7"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 178 - NCmel25 - 
FeaturePlot(all, features.plot = c("slc30a8", "slc38a11", "alkal2b", "si:dkey-24c2.9", "zdhhc2", "CLEC3A", "slc24a5", "tyr", "zgc:91968", "slc24a4a", "si:dkeyp-118a3.2", "prkar1b", "tspan10", "rgs16", "fmn2a", "emp3b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 179 - PharEpi2 - 
FeaturePlot(all, features.plot = c("shhb", "nkx3.3", "pitx1", "sp6", "shha", "foxa2", "ociad2", "inhbaa", "abi3b", "vgll4l", "pitx2", "nkx2.3", "afap1l1a", "frem2a", "tp63", "CABZ01024499.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 180 - PancExo - 
FeaturePlot(all, features.plot = c("CELA1 (1 of many).1", "si:dkey-266f7.9", "si:ch73-44m9.5", "pglyrp6", "BX908782.1", "CELA1 (1 of many).3", "CELA1 (1 of many).4", "si:ch211-255i20.3", "endou", "CELA1 (1 of many).2", "c6ast3", "sycn.3", "dnase1", "CELA1 (1 of many).5", "si:ch211-240l19.7", "syt15"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 181 - NCcranial5d - 
FeaturePlot(all, features.plot = c("pax1b", "fgfbp2a", "pax1a", "abtb2a", "mctp1a", "dlx4a", "fbln7", "sost", "cyp2ad2", "ecrg4a", "nog3", "dlx1a", "bmp2a", "gata2a", "dlx6a", "rgs5b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 182 - Peri2c - 
FeaturePlot(all, features.plot = c("si:dkey-56i24.1.1", "si:ch211-264e16.2", "si:dkey-239b22.2", "ponzr4", "zgc:163121", "wu:fj05g07", "si:dkey-9l20.3", "muc13a", "si:ch211-264e16.1", "irg1l", "si:ch211-153b23.4", "ponzr3", "ano9a", "jac10", "grk5", "zgc:123217"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 183 - Peri1b - 
FeaturePlot(all, features.plot = c("si:ch1073-155h21.1", "BX511250.1", "BX936456.1", "si:ch211-153b23.3", "si:dkeyp-67a8.4.1", "LO018208.1", "irg1l", "he1.3", "cyp2aa8", "prss60.2", "si:ch73-181m17.1", "slc35a3b", "ccl20a.3", "tex36", "cyp2aa11", "si:dkey-160o24.3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 184 - Macro12 - 
FeaturePlot(all, features.plot = c("si:dkey-32n7.4", "cx32.2", "CABZ01041494.1", "si:ch73-343l4.8", "entpd2a.1", "gpr84", "slc2a6", "plaua", "si:ch73-343l4.2", "fcer1g", "CABZ01080042.1", "si:dkey-27h10.2", "dicp3.1", "cd22", "MFAP4 (1 of many).9", "CABZ01088134.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 185 - NCxantho25 - 
FeaturePlot(all, features.plot = c("oacyl", "zgc:113142", "cyb561a3b", "bscl2l", "plin6", "si:dkey-251i10.2", "cax1", "slc22a7a", "tmem130", "aox5", "slc2a15a", "si:dkey-126g1.9", "slc2a11b", "slc2a15b", "mlpha", "pts"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 186 - Basal5b - 
FeaturePlot(all, features.plot = c("zgc:136254", "adamtsl7", "zgc:173443", "si:ch211-167j6.4", "wnt5a", "bhlha9", "si:ch211-182p11.1", "mslna", "BX004816.1", "si:ch211-251f6.6", "and3", "si:ch73-181m17.1", "si:dkey-56e3.2", "sp6", "zgc:123217", "NPNT (1 of many)"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 187 - Nonspecific1a - 
FeaturePlot(all, features.plot = c("six3b", "fabp11a", "fahd1", "znhit3", "zgc:194224", "thumpd3", "umps", "ppat", "dctpp1", "rrp8", "noc3l", "qtrt2", "cmss1", "myca", "exosc8", "polr1e"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 188 - BasalFin5b - 
FeaturePlot(all, features.plot = c("hhipl2", "si:ch211-76l23.4", "sod3b", "col17a1a", "plek2", "slc6a11a", "cxcl18a.1", "si:dkey-95h12.1", "si:dkey-119m7.8", "mmp30", "tkta", "cxl34b.11", "tnfsf10l4", "bgnb", "entpd3", "CABZ01068177.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 189 - PancAB - 
FeaturePlot(all, features.plot = c("gck", "scgn", "a1cf", "adm2a", "rprma", "c2cd4a", "renbp", "pdx1", "gcgb", "fev", "npas4a", "si:ch211-163l21.8", "si:ch211-113g11.6", "emb", "tmem63c", "ndufa4l2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 190 - Peri1c - 
FeaturePlot(all, features.plot = c("muc13a", "si:dkey-56i24.1.1", "si:dkey-239b22.2", "si:ch211-153b23.3", "tex36", "irg1l", "zgc:123217", "mia", "trim25l", "si:dkey-9l20.3", "si:ch211-153b23.4", "krt1-19d", "si:ch211-264e16.1", "rab11al", "si:dkey-160o24.3", "zgc:113442"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 191 - Parachord1 - 
FeaturePlot(all, features.plot = c("ndufa4l2a", "itga11a", "nav1b", "cd81b", "apof", "foxd5", "vstm4b", "has2", "CABZ01073265.1", "ndnfl", "foxl1", "vcana", "nkx3.2", "si:dkeyp-106c3.1", "pcolce2a", "zgc:162612"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 192 - FBDiff12 - 
FeaturePlot(all, features.plot = c("sim1a", "l1cama", "fezf1", "FP085414.1", "lhx5", "otpb", "uncx", "fezf2", "slc17a6b", "celf4", "otpa", "nrn1a", "adcyap1b", "nell2b", "adam22", "mpp2a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 193 - Nonspecific1b - 
FeaturePlot(all, features.plot = c("umps", "six3b", "exosc8", "ftsj3", "cmss1", "FP245462.1", "impdh1b", "dctpp1", "wdr12", "myca", "mtbl", "ppan", "paics", "pold2", "pus7", "chtf8"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 194 - SCDiff12c - 
FeaturePlot(all, features.plot = c("wnt4b", "spon1a", "pth1a", "cyr61l2", "tbata", "cfap126", "spata18", "nkx2.2b", "si:ch211-176l24.4", "cfap57", "cfap299", "armc4", "CABZ01072077.1", "cfap58", "nkx2.9", "zgc:113531"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 195 - MHBProg1 - 
FeaturePlot(allSUB, features.plot = c("pax5", "en2a", "en2b", "en1b", "sox21a", "pax2a", "cnpy1", "qdpra", "nanos1", "exosc8", "dctpp1", "dnajc2", "her8a", "sox19a", "pou3f3a", "hpf1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 196 - TasteBud - 
FeaturePlot(all, features.plot = c("si:dkeyp-92c9.4", "rgs1", "BX005256.1", "zgc:194948", "PLCB2", "CABZ01068499.1", "muc5.3", "muc5f", "gng13a", "trpm5", "avil", "ceacam1", "LO018550.2", "kcnk17", "zgc:158412", "prss60.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 197 - MusEntSmo - 
FeaturePlot(all, features.plot = c("kcne4", "mfap5", "myh11a", "mylka", "foxf1", "mylkb", "bgnb", "si:ch211-270g19.5", "acta2", "foxl1", "loxa", "BX908750.1", "lmod1b", "tagln", "BX088707.3", "CU914776.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 198 - HairCell - 
FeaturePlot(all, features.plot = c("tmc2a", "dnajc5b", "si:ch211-229d2.5", "si:dkey-33m11.8", "si:ch211-284k5.2", "si:ch73-261i21.5", "CR792457.1", "tmc2b", "atp6v1c2", "zmp:0000001088", "lhfpl5b", "baiap2l2b", "tspan1", "sh2d4ba", "zgc:171927", "si:dkey-103g5.3"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 199 - Hypophysis - 
FeaturePlot(all, features.plot = c("tmtops2a", "gbe1a", "lrrc58a", "ccka", "fgl2a", "FO681288.1", "ptger2b", "tubb6", "pmch", "tkta", "pitx1", "rerglb", "bco2a", "tnmd", "lmx1ba", "bco2l"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 200 - Lens12 - 
FeaturePlot(all, features.plot = c("crygm2d7", "crygmxl2", "crygm2d17.1", "crygm2d10", "crybb1l1", "crygm2d8.1", "crybb1l2", "crygm2d13", "cryba1l1", "cryba1b", "crybb1", "crygn2", "cryba2a", "cryba2b", "cryba4", "fabp11a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 201 - Vessel5 - 
FeaturePlot(all, features.plot = c("zmp:0000001102", "slc13a4", "slc22a7b.1", "si:ch211-76l23.7", "zgc:158423", "si:dkeyp-106c3.1", "slc47a1", "slc13a2", "plp1b", "slc47a2.1", "sat1a.1", "htr2cl1", "clec3ba", "CABZ01073265.1", "apof", "cnnm2b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 202 - SCNeurCilia12b - 
FeaturePlot(all, features.plot = c("pkd2l1", "pkd1l2a", "si:ch1073-70f20.1", "rnf220b", "grm2a", "c2cd4a", "syt6b", "fam19a1a", "urp1", "urp2", "flj13639", "si:ch211-258f14.2", "kcnf1a", "sst1.1", "dcdc2b", "nppc"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 203 - Arch2b - 
FeaturePlot(all, features.plot = c("lhx6", "gsc", "foxl1", "hoxb6a", "barx1", "foxf2a", "hoxb5b", "hoxb5a", "CABZ01075125.1", "tmeff2a", "prrx1b", "rspo2", "dlx1a", "meis3", "aldh1a2", "vasnb"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 204 - FinBud2 - 
FeaturePlot(all, features.plot = c("glsl", "angptl6", "eve1", "hoxb13a", "ptx3a", "hoxa13a", "si:ch211-14k19.8", "c1qtnf5", "hapln1b", "hoxc13a", "oscp1a.1", "adgrg6", "hoxa13b", "hoxc13b", "mxra8a", "loxa"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 205 - MusCard - 
FeaturePlot(allSUB, features.plot = c("lft2", "cx36.7", "nppa", "slc8a1a", "nppb", "adprhl1", "ryr2b", "tnnc1a", "myh6", "lmod2b", "myh7l", "lrrc10", "pln", "csrp3", "nkx2.5", "myh7"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 206 - Basal2b - 
FeaturePlot(all, features.plot = c("BX855590.1", "zgc:100997", "ponzr4", "cdh26.2", "mxc", "CU459012.1", "si:ch211-153b23.4", "si:dkey-95h12.1", "ubap1la", "cers3a", "col28a1a", "si:ch211-241e1.3", "col17a1b", "si:ch211-264e16.1", "grk5", "jac10"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 207 - HG2 - 
FeaturePlot(all, features.plot = c("BX000534.1", "BX322603.1", "vtcn1", "zmp:0000000951", "si:dkey-26g8.4", "zp3.2.1", "CU695215.2", "slc30a8", "fmn1", "LO017965.1", "cx30.9", "CT033796.2", "si:ch211-171h4.6", "mctp2b", "sytl4", "zgc:101785"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 208 - IonovH - 
FeaturePlot(all, features.plot = c("si:dkey-192d15.2", "ceacam1", "drd4-rs", "gcm2", "etf1a", "foxi3a", "slc4a1b", "prg4a", "ca15a", "agrp", "si:ch211-182p11.1", "cldn17", "zgc:193726", "si:ch73-359m17.5", "si:ch73-14h1.2", "scgn"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 209 - MusSkelSlow1b - 
FeaturePlot(all, features.plot = c("si:dkey-250i3.3", "mylk4a", "fhl1a", "smyhc3", "klhl41a", "foxd5", "CABZ01081777.1", "smyhc2", "CU633479.2", "alpk3b", "flncb", "chrng", "mmrn2b", "BX649294.1", "CR381686.5", "AL772146.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 210 - SpleenEpi - 
FeaturePlot(all, features.plot = c("ggt1a", "tnfa", "mmp13a", "lacc1", "lepb", "sult5a1", "plaua", "cd44a", "si:dkey-19b23.14", "csf3b", "nox1", "mmp13a.1", "si:ch211-39f2.3", "ms4a17a.4", "scpp8", "si:ch1073-110a20.7"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 211 - Epiphysis - 
FeaturePlot(all, features.plot = c("rdh20", "cidea", "plin1", "rrh", "CR792417.1", "slc16a8", "tmem72", "selenou1b", "slc4a5", "BX323820.1", "trpm1a", "inpp5kb", "slc13a4", "msnb", "slc22a6l", "cracr2ab"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 212 - Macro1 - 
FeaturePlot(all, features.plot = c("si:dkey-1c7.2", "si:ch211-225k7.5", "xcr1a.1", "FP085399.5", "gpr34b", "tlr1", "si:ch211-11c3.12", "si:dkey-27j5.7", "si:dkey-83f18.10", "CR626902.1", "spic", "si:ch73-343g19.4", "il1fma", "zgc:123107", "FP085399.2", "si:ch211-156b7.5"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 213 - Endothe1 - 
FeaturePlot(all, features.plot = c("f8", "vwf", "si:ch211-33e4.2", "ccm2l", "ecscr", "flt1", "tie1", "sele", "clec14a", "gpr182", "myct1b", "gata5", "myct1a", "edn2", "pecam1", "si:ch211-145b13.6"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 214 - IntestineEpi1 - 
FeaturePlot(all, features.plot = c("chia.3", "si:ch211-77g15.32", "wu:fa56d06", "ACOT12", "zgc:153968", "si:dkey-236e20.3", "mogat2", "apoea", "slc34a2a", "si:ch211-142d6.2", "slc6a19b", "slc13a2", "si:dkey-103j14.5", "pdzk1", "zgc:158846", "aqp8a.2"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 215 - Peri1d - 
FeaturePlot(all, features.plot = c("si:dkey-39a18.1", "si:dkeyp-67a8.4.1", "trim25l", "abca4a", "zgc:113442", "grhl3", "si:ch211-264f5.6", "chrna5", "dpys", "insl5a", "zbtb7a", "ponzr5", "BX323590.2", "LO017816.1", "noxo1a", "si:dkey-222f2.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 216 - Osteo - 
FeaturePlot(all, features.plot = c("bgna", "entpd5a", "si:ch211-106n13.3", "col5a2b", "sgms2a", "panx3", "ifitm5", "si:dkey-32e6.6", "si:ch211-170d8.8", "spp1", "enam", "bmp8a", "zgc:92162", "tgfb2l", "chst3b", "slc8a4b"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 217 - Hepato5c 
FeaturePlot(all, features.plot = c("si:dkey-79f11.10", "BX927210.1", "CABZ01000634.1", "si:ch211-113d11.8", "si:dkey-7f3.14", "FO834888.1", "CU856343.1", "gltpd2", "rln3a", "acod1", "soat2", "apoc4", "gpr84gpr84", "hp", "si:ch211-271e10.2", "c3b.1"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 218 - Hypochord - 
FeaturePlot(all, features.plot = c("si:ch211-157b11.8", "spon2a", "pappaa", "pgfb", "col8a1b", "mnx1", "ptx3a", "matn3b", "npr3", "cyr61l2", "angpt1", "loxl5b", "cd59", "aplnr2", "ism2a", "sim1a"), cols.use = c("light gray", "red"), reduction.use = "umap")
# cluster 219 - PGC - 
FeaturePlot(all, features.plot = c("tdrd7a", "dazl", "fkbp6", "zpcx", "tdrd12", "dnd1", "ca15b", "pld6", "adad1", "cpeb1b", "nanos3", "akap1a", "si:dkey-189g17.2", "CR382383.2", "zgc:112416", "si:ch211-226h8.11"), cols.use = c("light gray", "red"), reduction.use = "umap")

```
