---
title: "How I Installed Monocle3 Beta & Seurat 4 with Rv4.1.0"
author: "Shay Iyer"
date: "5/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

[Original installation instructions for Seurat]("https://satijalab.org/seurat/articles/install.html") \br
[Original installation instructions for Monocle3 Beta]("https://cole-trapnell-lab.github.io/monocle3/docs/installation/")

# Welcome!
Here are some instructions I wrote to set up our preferred versions of Seurat (v4) and Monocle (v3 alpha) for R with OSx for this project. \br
> Tip: copy/paste each chunk (after the curly brackets) into the R console or terminal (as needed)
```{r setup, eval=FALSE}
knitr::opts_chunk$set(
	include = TRUE
)
```

### Installing tidyverse, if you don't have it already

> Tip: You only ever need to install a package once with `packages.install("[package.as.string")`, but you need to load it using the `library(package_as_var)` function every time you start up R, and in every new RMarkdown file that you make (so that it can knit every time someone runs it)

```{r eval = FALSE}
install.packages("tidyverse")
```

### Load tidyverse
```{r eval = FALSE}
library(tidyverse)
```

### Installing Seurat
```{r eval = FALSE}
install.packages("Seurat")
```

### Installing Bioconductor
If you are running R Version 4.1.0, install Bioconductor 3.13. If not, upgrade to 4.1.0 before doing this next step (you can just download the right version from the CRAN website).
```{r eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
install.packages("BiocManager")
BiocManager::install(version = "3.13")
```


#### Installing helper packages
```{r eval = FALSE}
BiocManager::install(c('BiocGenerics', 'DelayedArray', 'DelayedMatrixStats',
                       'limma', 'S4Vectors', 'SingleCellExperiment',
                       'SummarizedExperiment', 'batchelor', 'Matrix.utils'))
```
Take note of non-fatal error messages!

`Update all/some/none? [a/s/n]: a` \br
Choose 'a' when prompted. If installation has already failed for these packages once, choose 'n'; take note of all packages, install/load as needed. \br
`Do you want to install from sources the package which needs compilation? (Yes/no/cancel) yes` \br
Choose 'yes' when prompted. If certain package installations had non-zero exit status, make a note of package names. Check if enabled in the Packages tab of RStudio. Install as needed, then load with `library(package-name)`. 

###  Installing Monocle 

#### Installing Homebrew

In Terminal:
```{bash eval = FALSE}
$ /bin/bash -c "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/HEAD/install.sh)" 
```

#### Installing gdal and sf

In RStudio, check if you have the 'sf' package. If not, you likely need to install the dependency 'gdal' for your Mac. Open Terminal for your Mac and do the following.

```{bash eval = FALSE}
brew install pkg-config
brew install gdal
```

Then return to R and run:
```{r eval = FALSE}
install.packages("sf", configure.args = "--with-proj-lib=/usr/local/lib/")
library(sf)
```


#### Installing/re-installing gfortran 
You probably need to install or reinstall gfortran for the Mac, but it only works if you download the dmg from the appropriate website rather than installing gcc with brew.

Return to terminal and type `which gfortran`. If a directory is returned, run `sudo rm -r /usr/local/gfortran /usr/local/bin/gfortran` to remove the current package. \br

Next, navigate to [this page]("https://github.com/fxcoudert/gfortran-for-macOS/releases") and find the appropriate .dmg file (the Monocle website says to download the tar.xz file and install manually, but the .dmg file is user-friendly, more manageable, and it works). Click on the "Assets" dropdown and download the appropriate .dmg for your osX. The iMac in SR401 runs Mojave; if you want to check on a Mac, click on the Apple logo (top left of the Menu Bar) and select "About this Mac". The OSX system should be listed. \br

Launch the .dmg file from your downloads and install. Then return to Terminal and type `which gfortran` once again; it should return a directory similar if not exactly the same as before. \br

#### Installing devtools, leidenbase, and monocle3 

```{r eval = FALSE}
install.packages("devtools")
```

```{r eval = FALSE}
devtools::install_github('cole-trapnell-lab/leidenbase')
```

If this works, allow yourself 5 seconds to cry with relief, then run: 

```{r eval = FALSE}
devtools::install_github('cole-trapnell-lab/monocle3')
```


### Loading the Seurat Object for Atlas for Zebrafish Development (Farnsworth et al., 2019)

#### Loading libraries
```{r eval = FALSE}
library(Seurat)
library(Matrix)
library(monocle3)
library(R.utils)
```

#### Getting the expression matrix and metadata from UCSC Cell Browser.
> IMPORTANT: this will take a large amount of time, and if your computer has an 8GB RAM, R will most likely return the error `resulting vector exceeds vector length limit`. This makes me think that there is a far better way to go about downloading the necessary data; *I suggest holding off on running the next two chunks of code unless you're using a lab computer*. 

```{r eval = FALSE}
require(Seurat)
require(data.table)
mat <- fread("https://cells.ucsc.edu/zebrafish-dev/exprMatrix.tsv.gz")
meta <- data.frame(fread("https://cells.ucsc.edu/zebrafish-dev/meta.tsv"), row.names = 1)
``` 

```{r eval = FALSE}
genes = mat[,1][[1]]
genes = gsub(".+[|]", "", genes)
mat = data.frame(mat[,-1], row.names=genes)
so <- CreateSeuratObject(counts = mat, project = "zebrafish-dev", meta.data=meta)
```

